Referee report checklist

### 2021-01-07 Revision/list.tex
revised mansucript and response to reviewers

Thank you for the opportunity to resubmit at \emph{International Journal of Forecasting}. Thank you to the reviewers for comments that led to an improved version of this manuscript. We address all of the reviewers' comments below. An outlines of each change made or a rebuttal is provided for all of the reviewer's comments.

@@

\response{We include another example of forecasting the stock price of Apple Inc. during MacBook release in 2020 in Section 5.2 of the revised manuscript. Our method nearly perfectly recovers its stock price of the day after the release date. The donor pool constructed includes three time series of  Apple inc.'s stock price during MacBook release in the past three years. In this example, the shock is with precedent and our method works well because Apple Inc. is a well-established company that is not expected to reform its products a lot. As a result, knowledge from past shocks can bring insights into the future shocks. This example is representative for applying our methods to the time series that are to experience a shock that is with precedent in the past. In contrast, the example of Conoco Phillips is without precedent. In the past, Conoco Phillips  did not experience oil supply shock and financial crisis shock caused by  pandemic. In this example, our method is better than the original forecast though it cannot fully recover the stock price. We hope that the addition of the Apple example helps to generate confidence in our approach.
}

@@

\response{We go for a plug-in approach. If we can estimate $\mu_{\alpha}$ well, the results should hold with high probability. Section 3.2 is dedicated to this estimation problem. Using plug-in approaches, we get a decision rule to determine whether the scalar adjustment will be beneficial with correctness probability $p$. Section 3.3 details the leave-one-out cross validation procedures, which are tailored to our setup, to estimate $p$. As a result, users can be informed about the credibility of our methods} \\

@@

%Lastly,  greater number of bootstrap replication $B$ is preferred. Usually, $B = 200$ is sufficient. 
Ideally, $k=n$ is preferred. However, if the data size is large such that $k=n$ is computationally expensive, we found that $k = 5$ or $k = 10$ works well. In practice, $(k+1) B$ number of bootstrap replications are implemented to complete the evaluation, where $k B$ is from LOOCV to estimate the correctness parameter $p$ and $B$ is from ordinary bootstrap using the whole donor pool. \\

} \\

>>>>

Thank you for the opportunity to resubmit at \emph{International Journal of Forecasting}. Thank you to the reviewers for comments that led to an improved version of this manuscript. We address all of the reviewers' comments below. An outline of each change made or a rebuttal is provided for all of the reviewers' comments.

@@

\response{We include another example of forecasting the stock price of Apple Inc. during MacBook release in 2020 in Section 5.2 of the revised manuscript. \textcolor{red}{Our forecast is very close to the stock price of the day after the release date.} The donor pool constructed includes three time series of  Apple inc.'s stock price during MacBook release in the past three years. In this example, the shock is with precedent and our method works well because Apple Inc. is a well-established company that is not expected to reform its products a lot. As a result, knowledge from past shocks can bring insights into the future shocks. This example is representative for applying our methods to the time series that are to experience a shock that is with precedent in the past. In contrast, the example of Conoco Phillips is without precedent. In the past, Conoco Phillips  did not experience oil supply shock and financial crisis shock caused by  pandemic. In this example, our method is better than the original forecast though it cannot fully recover the stock price. We hope that the addition of the Apple example helps to generate confidence in our approach.}

@@

\response{We go for a plug-in approach. If we can estimate $\mu_{\alpha}$ well, the results should hold with high probability. Section 3.2 is dedicated to this estimation problem. Using plug-in approaches, we get a decision rule to determine whether the scalar adjustment will be beneficial with correctness probability $p$. Section 3.3 details the leave-one-out cross validation procedures, which are tailored to our setup, to estimate $p$. As a result, users can be informed about the credibility of our methods.} \\

@@

%Lastly,  greater number of bootstrap replication $B$ is preferred. Usually, $B = 200$ is sufficient. 
Ideally, $k=n$ is preferred. However, if the data size is large such that $k=n$ is computationally expensive, we found that $k = 5$ or $k = 10$ works well. In practice, $(k+1) B$ number of bootstrap replications are implemented to complete the evaluation, where $k B$ is from LOOCV to estimate the correctness parameter $p$ and $B$ is from ordinary bootstrap using the whole donor pool. } \\
